Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-13 text/paper2/ms.tex
sharpen intro paragraph

Cosmological simulations of galaxy formation in the $\Lambda$CDM paradigm predict dark matter halos that (1) are permeated with substructure on many scales, (2) are triaxial in shape, and (3) have density profiles and shapes that vary with radius \citep{dubinski91, jing02, kuhlen07, veraciro11}. Dark-matter-only simulations seem to produce strongly triaxial halos, but including baryons tends to soften the triaxiality in the inner galaxy [through a combination of adiabatic contraction and energetic feedback \citep[see recent discussion by][]{pontzen12} TODO: modify previous sentence bc in PW\&J 2013]. These [...] may lead to radially-dependent axis ratios, halo orientation, and density profiles.

>>>>

Cosmological simulations of galaxy formation in the $\Lambda$CDM paradigm predict dark matter halos that (1) are permeated with substructure on many scales, (2) are triaxial in shape, and (3) have density profiles and shapes that vary with radius \citep{dubinski91, jing02, kuhlen07, veraciro11}. Dark-matter-only simulations produce strongly triaxial halos \citep{} with large density variations \citep{zemp09}. Including baryons tends to soften the triaxiality in the inner galaxy through energetic feedback \citep[e.g.,][]{pontzen12} but does not erase the clumpy, triaxial nature of the outer halo. This leads to radially-dependent axis ratios and orientation, density profiles, and smoothness, thus predicting complicated, non-intregrable potential forms for Milky Way-like galaxies.
